Outline flowCore paper

### 2008-04-30 paper/manuscript.tex
more specific about sotware imports now
git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/flowCore@31449 bc3139a8-67e5-0310-9ffc-ced21a209358
fixed some typos
git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/flowCore@31450 bc3139a8-67e5-0310-9ffc-ced21a209358

Static gating for all samples in a high-throughput flow cytometry
experiment is often not an option, since the measured variables tend
to vary between different treatments or over time. Automated or
data-driven gating tries to estimate the gating regions from the
underlying data, thus providing a fast objective solution to the
analysis of potentially very large and diverse data sets
\cite{lo2008agf}. One of the automated gating methods implemented in
flowCore is based on identifying areas of significant curvature in a
kernel density estimate of the data (\citep{wand2008}). Assuming that
the regions of interest are of high density, the software is able to
reliably detect them in either the one ore the two-dimensional density
landscape. Kernel density estimation is a well-known problem in
statistical computing, and a lot of effort has been invested in the
development of good software to address it. The modular design of R,
Bioconductor and flowCore allows to easily integrate these existing
solutions into our framework. Instead of re-writing existing code, we
are able to include it via the well tested distribution mechanism
provided by R's software package system. This process is
bi-directional, and all funtionality implemented in flowCore is
available to other package authors, as we have seen with the
afore-mentioned flowClust package.

>>>>

Static gating for all samples in a high-throughput flow cytometry
experiment is often not an option, since the measured variables tend
to vary between different treatments or over time. Automated or
data-driven gating tries to estimate the gating regions from the
underlying data, thus providing a fast objective solution to the
analysis of potentially very large and diverse data sets
\cite{lo2008agf}. One of the automated gating methods implemented in
flowCore is based on identifying areas of significant curvature in a
kernel density estimate of the data \citep{wand2008}. Assuming that
the regions of interest are of high density, the software is able to
reliably detect them in either the one ore the two-dimensional density
landscape. Kernel density estimation is a well-known problem in
statistical computing, and a lot of effort has been invested in the
development of good software to address it. The modular design of R,
Bioconductor and flowCore allows to easily integrate these existing
solutions into our framework. In this example, we directly use R code
from the feature package developed by Wand et al. Instead of
re-writing existing code, we are able to include it via the well
tested distribution mechanism provided by R's software package
system. This process is bi-directional, and all funtionality
implemented in flowCore is available to other package authors, as we
have seen with the afore-mentioned flowClust package.
